---
title: "World's GDP Vs. Life Expectancy"
author: "Sovann Prey"
date: "4/26/2021"
runtime: shiny
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## App Overview and Function
The app will visualize the World's GDP vs. Life Expentance for all the countries in different years using the Gapminder datasets.

The app has been developed using Shiny application from RStudio. The source code of the application can be found here.

The applicaton allows the users to:

- Plot the data in a scatter plot (GDP vs. Life Expectancy)
- Create a set of parameters, such as year and continent, for data visualization.
- Customize data visualization.
- Generate a table for the data
- Download the data

## Application Interface
The web app contains two sections: configuration and visualization part.

- **Configuration**: allows the users to filter the data and configure visualization of the data.
- **Visualization**: allows the users to see the (filtered) data being visualized in the form of graph/plot and table.

## Application Interface Details
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(shiny)
library(shinycustomloader)
library(colourpicker)
library(ggplot2)
library(plotly)
library(gapminder)


shinyApp(

  # Define UI for application that draws a histogram
  shinyUI(fluidPage(
    
    # Application title
    titlePanel("World's GDP and Life Expectancy"),
    
    # Sidebar with a slider input for number of bins
    sidebarLayout(
      sidebarPanel(
        
        textInput("title", "Title (for the graph)", "GDP vs. life exp"),
        
        selectInput("year", "Year",
                    choices = c("All", unique(gapminder$year))),
        
        selectInput("continent", "Continent",
                    choices = c("All", levels(gapminder$continent))),
        
        sliderInput(inputId = "life", label = "Life expectancy",
                    min = 0, max = 120,
                    value = c(40, 90)),
        
        numericInput("size", "Point size", 1, 1),
        
        colourInput("color", "Point color", value = "#0934ab"),
        
        downloadButton("download_data")
        
      ),
      
      # Show a plot of the generated distribution
      mainPanel(
        
        # Output: Tabset with plot, summary, and table
        tabsetPanel(type = "tabs",
                    
                    tabPanel("Graph", withLoader(plotlyOutput("plot")) ),
                    tabPanel("Table", withLoader(DT::dataTableOutput("table")))
        )
      )
    )
  )),
  
  # Define server logic required to draw a histogram
  shinyServer(function(input, output) {
    
    filtered_data <- reactive({
      data <- gapminder
      data <- subset(
        data,
        lifeExp >= input$life[1] & lifeExp <= input$life[2]
      )
      
      if (input$continent != "All") {
        data <- subset(
          data,
          continent == input$continent
        )
      }
      
      if(input$year != "All"){
        data <-subset(
          data,
          year == input$year
        )
      }
      
      data
    })
    
    output$table <- DT::renderDataTable({
      data <- filtered_data()
      data
    })
    
    output$download_data <- downloadHandler(
      filename = function() {
        paste("gapminder-exported-data-", Sys.Date(), ".csv", sep="")
      },
      content = function(file) {
        write.csv(filtered_data(), file)
      }
    )
    
    output$plot <- renderPlotly({
      
      ggplotly({
        data <- filtered_data()
        
        p <- ggplot(data, aes(gdpPercap, lifeExp)) +
          geom_point(size = input$size, col = input$color) +
          scale_x_log10() +
          ggtitle(input$title) +
          geom_hline(yintercept = mean(data$lifeExp), color="red")
        
        p
      })
    })
  })


)

```

## Gapminder Datasets
The application is based on the [Gapminder](https://cran.r-project.org/web/packages/gapminder/README.html) datasets.

```{r, echo=TRUE, warning=FALSE}
library(gapminder)
str(gapminder)
```

Click this [link]() to access the web app. Source code is [here](https://github.com/preysovann/dvdp2/tree/master/myLittleShinyApp).

